The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-11-22 OA.tex
Prepare draft for submission

\begin{center}
	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
	\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira}
\end{center}

@@

\section{ }
\vspace{.2in}

\vspace{.1in}
\subsection{Internal Validity}

@@

\begin{table}[H]
\caption{Number of pawns balance before and after the experiment}
\label{num_pawns_bal}
\begin{center}
\scriptsize{\input{./Tables/num_pawns_bal.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{num\_pawns\_bal.do}
\end{table}
\end{comment}
%\todo[inline]{removed}

@@

@@

\newpage
\subsection{Some more evidence of overconfidence}

@@

\begin{figure}[H]
        \caption{Survival graph}
    \label{survival_graph}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Ended contract}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure}     
    \end{center}
     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}

@@

\vspace{.2in}
\subsection{Learning}

@@

This table presents information about borrowers' \emph{future} pawning behavior.
Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
Each row presents a difference in mean commitment take-up rates and associated standard errors.
The first row (ATE) compares borrowers who were initially assigned to forced commitment against those were assigned to the control condition.
The second row (ITT) compares borrowers who were initially assigned to the choice commitment condition to those who were not.
Whereas column (1) conditions on the (endogenously) selected sample of borrowers who return to pawn again, column (2) considers the full sample by re-defining the ``outcome'' to be an indicator for whether a borrower pawned again on a day when choice was offered \emph{and} chose commitment.

@@

\vspace{.3in}
\subsection{First order stochastic dominance} \label{App_FOSD}
\normalsize
\vspace{.2in}

%\todo[inline]{Presumably we want to cut some of this text? In the body of the text we don't get into this in such detail.}
%We plot the empirical distribution of financing cost $F_{commitment}(FC)$ and of the status quo contract, $F_{sq}(FC)$. Framed as a choice among cost distributions.

\vspace{.2in}
\begin{figure}[H]
        \caption{Empirical CDF of Financial Cost: Forced commitment vs Control}
    \label{ecdf_fc}

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure plots plots the empirical CDF of experimental outcomes separately for the control / status quo (dashed) and forced commitment contracts (solid). In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit. In each case, the empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo. This can be seen by examining the dotted line at the bottom of panels (a) and (b), which shows the difference $(\text{Control} - \text{Commitment})$. 
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{fosd_ecdf.do}}
\end{figure}

\begin{figure}[H]
        \caption{Distribution of treatment effects under rank invariance.}
    \label{te_rankinvariance}

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure show the distribution of treatment effects under rank invariance
    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{te_rankinvariance.do}}
\end{figure}

@@

\section{Testing for heterogeneity}
\label{append:chernozhukov}
If the treatment effects $Y_{i1} - Y_{i0}$ are constant across $i$, then we must have
\[
\text{ATE}(X_i) \equiv \mathbbm{E}[Y_{i1} - Y_{i0} |X_i] = \mathbbm{E}[Y_{i1} - Y_{i0}] \equiv \text{ATE}
\]
for any covariates $X_i$ that vary across $i$. If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
This avoids inferential problems that could arise from correlated unobservables within clusters.
In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) of 0.43.
Thus we easily reject the null hypothesis of homogeneous treatment effects.

@@

@@

This section describes the testable implications of our exclusion restrictions: \eqref{eq:exclusion0} and \eqref{eq:exclusion1} from Section \ref{sec:potentialOutcomes}. 
To consider possible violations of these conditions, it is helpful to introduce some additional notation.
As above, let $Y_0 \equiv Y(d=0,z=0)$ and $Y_1 \equiv Y(d=1,z=1)$ denote the potential outcomes under \emph{forced treatment}: $Y_0$ is the potential outcome when forced into the status quo contract and $Y_1$ when forced into the commitment contract. 
Further let $Y_{0,2} \equiv Y(d=0,z=2)$ and $Y_{1,2} \equiv Y(d=1,z=2)$ denote the potential outcomes under \emph{free choice of treatment}: $Y_{0,2}$ is the potential outcome when choosing the status quo contract and $Y_{1,2}$ when choosing the commitment contract. 
Using this notation, \eqref{eq:exclusion0} becomes $Y_0 = Y_{0,2}$ and while \eqref{eq:exclusion1} becomes $Y_1 = Y_{1,2}$.
If we do not impose this pair of equalities, part (iii) of Assumption \ref{assump:randchoice} becomes 
\[
Y = \mathbbm{1}(Z =0) Y_{0} + \mathbbm{1}(Z = 1)  Y_{1}  + \mathbbm{1}(Z = 2) \left[(1 - C) Y_{0,2} + C Y_{1,2} \right]
\]
but parts (i) and (ii) continue to hold.
Accordingly, parts (i)--(iii) of Lemma \ref{lem_randchoice} are unchanged, while parts (iv) and (v) become
\[
\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_{0,2}|C=0), \quad
\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_{0,1}|C=1).
\]
Using these expressions, the testable restrictions we consider here are as follows:
\begin{align}
\label{eq:exclusion_append0}
\mathbbm{E}(Y_0|C=0) &= \mathbbm{E}(Y_{0,2}|C=0) \\
\label{eq:exclusion_append1}
\mathbbm{E}(Y_1|C=1) &= \mathbbm{E}(Y_{1,2}|C=1).
\end{align}
Equation \ref{eq:exclusion_append0} is a restriction on the average potential outcomes of non-choosers that we use to point identify the TUT effect.
It says that someone who \emph{would} choose the control condition when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to the control condition.
Equation \ref{eq:exclusion_append1} is a restriction on the average potential outcomes of choosers that we use to point identify the TOT effect.
It says that someone who \emph{would} choose the commitment contract when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to this condition.
Because they refer to different groups of people, either of \eqref{eq:exclusion_append0}  and \eqref{eq:exclusion_append1} could hold when the other is violated.
For this reason we consider each in turn.
Our approach is closely related arguments from \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
As such, the following is a heuristic explanation rather than a fully-rigorous proof.
See the aforementioned papers for more details of how to make this argument fully rigorous.

Consider first \eqref{eq:exclusion_append0}.
Let $p \equiv \mathbbm{P}(C=1) = \mathbbm{P}(D=1|Z=2)$ denote the share of choosers in the population.
This value is point identified regardless of whether the exclusion restriction holds.
Because $Z$ was randomly assigned, a fraction $p$ of borrowers with $Z=0$ are choosers while the remaining $(1-p)$ are non-choosers.
It follows that, regardless of whether the exclusion restriction holds, the observed distribution of $Y|Z=0$ is a mixture of $Y_0|C=0$ and $Y_0|C=1$ with mixing weights $(1-p)$ and $p$.
This allows us to construct a pair of bounds for $\mathbb{E}(Y_0|C=0)$ as follows.
The non-choosers must lie \emph{somewhere} in the distribution of $Y|Z=0$.
Consider the two most extreme possibilities: they could occupy the bottom $(1-p)\times 100\%$ of the distribution or the top $(1-p)\times 100\%$ of the distribution.
For this reason, computing the average of the the \emph{truncated} distribution of $Y|Z=0$, cutting out the top $p\times 100\%$, provides a lower bound for the average of $Y_0$ among non-choosers.
Similarly, cutting out the bottom $p \times 100\%$ provides an upper bound.
Let $y^0_{1-p}$ denote the $(1-p)$ quantile of $Y|Z=0$ and $y^0_{p}$ denote the $p$ quantile of the same distribution.
Using this notation, the bounds are given by
\[
\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y_0|C=0) \leq \mathbb{E}\left(Y|Z=0, Y \leq y^0_p\right) 
\]
These bounds do not rely on the exclusion restriction.
Under Equation \ref{eq:exclusion_append0}, however, we know that $\mathbb{E}(Y_0|C=0)=\mathbb{E}(Y|D=0,Z=2)$.
Therefore, if the exclusion restriction for non-choosers holds, we must have
\begin{equation}
\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y|D=0,Z=2) \leq \mathbb{E}\left(Y|Z=0, Y \leq y^0_p\right).
\label{eq:testable0}
\end{equation}
Equation \ref{eq:testable0} provides a pair of testable implications of \eqref{eq:exclusion_append0}.
If either inequality is violated, then the exclusion restriction for non-choosers fails.

>>>>

\begin{center}
	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
	\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
\end{center}

@@

\section{Treatment Explanation Materials and Pictures}
\vspace{.2in}

\subsection{Materials}

\begin{figure}[H]
     \caption{Contract Terms Summary}
    \label{PaperSlip}
    \begin{center}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Receipt for client}
     %   \centering
        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
    %\end{subfigure}

    %\vspace{3ex}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Personal promise signed by client}
     %   \centering
    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
    %\end{subfigure}
    \end{center}
    \scriptsize
        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity). We want to highlight the salience of some items. First the title clearly indicated which contract the client has (arrow 1). Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2). Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month. %The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient. It emphasizes that the client is giving his word, and that the promise is not a legal document.
\end{figure}

\begin{figure}[H]
     \caption{Explanatory Material}
    \label{ExplanatoryMaterial}
    \begin{center}
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
\end{figure}

@@

\begin{comment}
\\
\begin{table}[H]
\caption{Number of pawns balance before and after the experiment}
\label{num_pawns_bal}
\begin{center}
\scriptsize{\input{./Tables/num_pawns_bal.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{num\_pawns\_bal.do}
\end{table}
\end{comment}
%\todo[inline]{removed}

@@

\newpage
\subsection{Descriptives consistent with overconfidence}

\vspace{.1in}
\section{Internal Validity}

@@

@@

\begin{figure}[H]
        \caption{Survival graph}
    \label{survival_graph}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Ended contract}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure}     
    \end{center}
     \scriptsize  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}

@@

\vspace{.2in}
\subsection{Learning}
\normalsize
Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment. Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm. Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error. The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms. In each case, there is no statistically discernible difference in the rates of commitment take-up. Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation. For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment. This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow). The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two. Again, there is no statistically discernible difference in commitment take-up rates in either row. While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.

@@

Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
Each row presents a difference in mean commitment take-up rates and associated standard errors.
The first row (ATE) compares borrowers who were initially assigned to forced commitment against those were assigned to the control condition.
The second row (ITT) compares borrowers who were initially assigned to the choice commitment condition to those who were not.
Whereas column (1) conditions on the (endogenously) selected sample of borrowers who return to pawn again, column (2) considers the full sample by re-defining the ``outcome'' to be an indicator for whether a borrower pawned again on a day when choice was offered \emph{and} chose commitment.

@@

@@

\section{Heterogeneity and Bounds}

\subsection{Testing for heterogeneity}
\label{append:chernozhukov}
If the treatment effects $Y_{i1} - Y_{i0}$ are constant across $i$, then we must have
\[
\text{ATE}(X_i) \equiv \mathbbm{E}[Y_{i1} - Y_{i0} |X_i] = \mathbbm{E}[Y_{i1} - Y_{i0}] \equiv \text{ATE}
\]
for any covariates $X_i$ that vary across $i$. If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
This avoids inferential problems that could arise from correlated unobservables within clusters.
In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) standard error of 0.43.
Thus we easily reject the null hypothesis of homogeneous treatment effects.

@@

\subsection{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}

\vspace{.3in}
\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in APR\%}
    \label{fan_park_bounds}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize
    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
    This is greater than the share of borrowers who chose commitment: 11\%.
%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
\end{figure}

\vspace{.2in}
\begin{figure}[H]
        \caption{Empirical CDF: Forced commitment vs Control FOSF}
    \label{ecdf_fc}

    \begin{center}
        \begin{subfigure}{0.49\textwidth}
         \caption{APR benefit}
         \centering
         \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
     \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure plots the empirical CDF of experimental outcomes separately for the control (status quo) in dashes, and forced commitment contracts (solid). In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit. 
    The empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo. This can be seen by examining the dotted line, which shows the difference $(\text{Control} - \text{Commitment})$. 
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{fosd_ecdf.do}}
\end{figure}

\vspace{.2in}
\begin{figure}[H]
        \caption{Distribution of treatment effects under rank invariance.}
    \label{te_rankinvariance}

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from 
    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{te_rankinvariance.do}}
\end{figure}

@@

This section describes the testable implications of our exclusion restrictions: \eqref{eq:exclusion0} and \eqref{eq:exclusion1} from Section \ref{sec:potentialOutcomes}. 
To consider possible violations of these conditions, it is helpful to introduce some additional notation.
As above, let $Y_0 \equiv Y(d=0,z=0)$ and $Y_1 \equiv Y(d=1,z=1)$ denote the potential outcomes under \emph{forced treatment}: $Y_0$ is the potential outcome when forced into the status quo contract and $Y_1$ when forced into the commitment contract. 
Further let $Y_{0,2} \equiv Y(d=0,z=2)$ and $Y_{1,2} \equiv Y(d=1,z=2)$ denote the potential outcomes under \emph{free choice of treatment}: $Y_{0,2}$ is the potential outcome when choosing the status quo contract and $Y_{1,2}$ when choosing the commitment contract. 
Using this notation, \eqref{eq:exclusion0} becomes $Y_0 = Y_{0,2}$ and while \eqref{eq:exclusion1} becomes $Y_1 = Y_{1,2}$.
If we do not impose this pair of equalities, part (iii) of Assumption \ref{assump:randchoice} becomes 
\[
Y = \mathbbm{1}(Z =0) Y_{0} + \mathbbm{1}(Z = 1)  Y_{1}  + \mathbbm{1}(Z = 2) \left[(1 - C) Y_{0,2} + C Y_{1,2} \right]
\]
but parts (i) and (ii) continue to hold.
Accordingly, parts (i)--(iii) of Lemma \ref{lem_randchoice} are unchanged, while parts (iv) and (v) become
\[
\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_{0,2}|C=0), \quad
\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_{0,1}|C=1).
\]
Using these expressions, the testable restrictions we consider here are as follows:
\begin{align}
\label{eq:exclusion_append0}
\mathbbm{E}(Y_0|C=0) &= \mathbbm{E}(Y_{0,2}|C=0) \\
\label{eq:exclusion_append1}
\mathbbm{E}(Y_1|C=1) &= \mathbbm{E}(Y_{1,2}|C=1).
\end{align}
Equation \ref{eq:exclusion_append0} is a restriction on the average potential outcomes of non-choosers that we use to point identify the TUT effect.
It says that someone who \emph{would} choose the control condition when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to the control condition.
Equation \ref{eq:exclusion_append1} is a restriction on the average potential outcomes of choosers that we use to point identify the TOT effect.
It says that someone who \emph{would} choose the commitment contract when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to this condition.
Because they refer to different groups of people, either of \eqref{eq:exclusion_append0}  and \eqref{eq:exclusion_append1} could hold when the other is violated.
For this reason we consider each in turn.
Our approach is closely related to arguments from \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
As such, the following is a heuristic explanation rather than a fully-rigorous proof.
See the aforementioned papers for more details of how to make this argument fully rigorous.

Consider first \eqref{eq:exclusion_append0}.
Let $p \equiv \mathbbm{P}(C=1) = \mathbbm{P}(D=1|Z=2)$ denote the share of choosers in the population.
This value is point identified regardless of whether the exclusion restriction holds.
Because $Z$ was randomly assigned, a fraction $p$ of borrowers with $Z=0$ are choosers while the remaining $(1-p)$ are non-choosers.
It follows that, regardless of whether the exclusion restriction holds, the observed distribution of $Y|Z=0$ is a mixture of $Y_0|C=0$ and $Y_0|C=1$ with mixing weights $(1-p)$ and $p$.
This allows us to construct a pair of bounds for $\mathbb{E}(Y_0|C=0)$ as follows.
The non-choosers must lie \emph{somewhere} in the distribution of $Y|Z=0$.
Consider the two most extreme possibilities: they could occupy the bottom $(1-p)\times 100\%$ of the distribution or the top $(1-p)\times 100\%$ of the distribution.
For this reason, computing the average of the \emph{truncated} distribution of $Y|Z=0$, cutting out the top $p\times 100\%$, provides a lower bound for the average of $Y_0$ among non-choosers.
Similarly, cutting out the bottom $p \times 100\%$ provides an upper bound.
Let $y^0_{1-p}$ denote the $(1-p)$ quantile of $Y|Z=0$ and $y^0_{p}$ denote the $p$ quantile of the same distribution.
Using this notation, the bounds are given by
\[
\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y_0|C=0) \leq \mathbb{E}\left(Y|Z=0, Y \geq y^0_p\right) 
\]
These bounds do not rely on the exclusion restriction.
Under Equation \ref{eq:exclusion_append0}, however, we know that $\mathbb{E}(Y_0|C=0)=\mathbb{E}(Y|D=0,Z=2)$.
Therefore, if the exclusion restriction for non-choosers holds, we must have
\begin{equation}
\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y|D=0,Z=2) \leq \mathbb{E}\left(Y|Z=0, Y \geq y^0_p\right).
\label{eq:testable0}
\end{equation}
Equation \ref{eq:testable0} provides a pair of testable implications of \eqref{eq:exclusion_append0}.
If either inequality is violated, then the exclusion restriction for non-choosers fails.
In our experiment, $\widehat{p} = \widehat{\mathbbm{P}}(D=1|Z=2) = 0.11$. For the APR outcome we estimate
\[
\widehat{\mathbbm{E}}(Y_\text{APR}|Z=0,Y_\text{APR}\leq y^0_{0.89}) = 0.48, \quad
\widehat{\mathbbm{E}}(Y_\text{APR}|Z=0, Y_\text{APR}\geq y^0_{0.11}) = 0.62.
\]
Since $\widehat{\mathbbm{E}}(Y_\text{APR}|D=0,Z=2) = 0.58$ falls between these bounds, we find no evidence against the exclusion restriction for non-choosers. 
Repeating this exercise for the financial cost outcome, we see that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=0,Z=2) = 973$ likewise falls between 
\[
\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0,Y_\text{FC}\leq y^0_{0.89}) = 626, \quad
\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0, Y_\text{FC}\geq y^0_{0.11}) = 1046 
\]
so we again find no evidence against the exclusion restriction for non-choosers.
